Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-02-01 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added Bocconi lecture
Added outline of lecture + paper pres

\newenvironment{stepenumerate}{\begin{enumerate}[<+->]}{\end{enumerate}}
\newenvironment{stepitemize}{\begin{itemize}[<+->]}{\end{itemize} }
\newenvironment{stepenumeratewithalert}{\begin{enumerate}[<+-| alert@+>]}{\end{enumerate}}
\newenvironment{stepitemizewithalert}{\begin{itemize}[<+-| alert@+>]}{\end{itemize} }
\usetheme{Boadilla}

@@

%------------------------------------------------
%	PRESENTATION BASICS
%------------------------------------------------

@@

\author[Dalton, R{\"u}schenp{\"o}hler, Uras, and Zia]
{
Patricio S. Dalton\inst{1}\
Julius R{\"u}schenp{\"o}hler\inst{2}
Burak Uras\inst{1}\\and
Bilal Zia\inst{3}
}

\institute[]
{
\inst{1} Tilburg University\\
\bigskip
\inst{2} CEGA, UC Berkeley\\
\bigskip
\inst{3} The World Bank\\
}

@@

\author[Dalton, R{\"u}schenp{\"o}hler, Uras, and Zia]
{
Patricio S. Dalton\inst{1}\
Julius R{\"u}schenp{\"o}hler\inst{2}
Burak Uras\inst{1}\\and
Bilal Zia\inst{3}
}

\institute[]
{
\inst{1} Tilburg University\\
\bigskip
\inst{2} CEGA, UC Berkeley\\
\bigskip
\inst{3} The World Bank\\
}

%------------------------------------------------
%	PRESENTATION SLIDES
%------------------------------------------------

@@

%\begin{frame}
%\frametitle{Overview}
%\tableofcontents[hideallsubsections]
%\end{frame}

>>>>

\newenvironment{stepenumerate}{\begin{enumerate}[<+->]}{\end{enumerate}}
\newenvironment{stepitemize}{\begin{itemize}[<+->]}{\end{itemize} }
\newenvironment{stepenumeratewithalert}{\begin{enumerate}[<+-| alert@+>]}{\end{enumerate}}
\newenvironment{stepitemizewithalert}{\begin{itemize}[<+-| alert@+>]}{\end{itemize} }

%\usetheme{Boadilla}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\usetheme[right]{Berkeley}
\setbeamercolor{sidebar}{bg=blue}

@@

\title[Skills, Practices, and Aspirations of Small Firms in LMICs]{Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings}
\author[R{\"u}schenp{\"o}hler]{Julius R{\"u}schenp{\"o}hler\inst{*}}
\institute[]{\inst{*} UC Berkeley, CEGA}
\date{March 04, 2021}

\setbeamertemplate{sidebar right}{}

\setbeamertemplate{sidebar right}[sidebar theme]

%\begin{frame}
%\frametitle{Overview of the Lecture}
%\tableofcontents[hideallsubsections]
%\end{frame}

\AtBeginSection
{\begin{frame}{Overview}
\tableofcontents[currentsection,hideothersubsections]
\end{frame}}

%\begin{document}

\section{\textbf{PART I: Lecture} \\ \quad \emph{Business Practices}}

\subsection{Business Practices Around the World}

\begin{frame}
\frametitle{?}
	\begin{itemize}
	\item Bloom and van Reenen (2010): Business practices, motivation
	\vspace{0.2in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Heterogeneity in Business Practices}
	\begin{itemize}
	\item Bloom and van Reenen (2010): Heterogeneity
	\vspace{0.2in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Value-Added of Business Practices}
	\begin{itemize}
	\item Bloom and van Reenen (2010): Correlation with productivity
	\vspace{0.2in}
	\end{itemize}
\end{frame}

%---------------------

\begin{frame}
\frametitle{Business Practices of Small Firms}
	\begin{itemize}
	\item McKenzie and Woodruff (2017): Heterogeneity and predictiveness
	\vspace{0.2in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Business Practices of Small Firms}
	\begin{itemize}
	\item McKenzie and Woodruff (2017): Example categories and practices
	\vspace{0.2in}
	\end{itemize}
\end{frame}

%---------------------

\begin{frame}
\frametitle{Best Practices for Small Firms}
	\begin{itemize}
	\item McKenzie and Woodruff (2017): Portable best practices
	\vspace{0.2in}
	\end{itemize}
\end{frame}

\subsection{Classical MSME Training}

\begin{frame}
\frametitle{History and Prevalence}
	\begin{itemize}
	\item At least \textcolor{red}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; McKenzie, 2020)
	\vspace{0.1in}
	\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity
	\vspace{0.2in}
	\item Examples: Start and Improve Your Business (ILO), Business Edge (IFC), \textcolor{red}{ELSE??}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

%----------------------

\begin{frame}
\frametitle{Typical Training Program}
	\begin{itemize}
	\item Content %\textcolor{}{}
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Typical Training Program}
	\begin{itemize}
	\item Delivery %\textcolor{}{}
	\vspace{0.1in}
	\end{itemize}
\end{frame}

%---------------------

\begin{frame}
\frametitle{Impact on Businesses}
	\begin{itemize}
	\item First wave (Karlan and Valdivia, 2011, etc.)
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Impact on Businesses}
	\begin{itemize}
	\item Econometric and implementation issues (McKenzie and Woodruff, 2014)
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Impact on Businesses}
	\begin{itemize}
	\item Recent evaluations (McKenzie, 2020)
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\subsection{Extensions of the Classical Approach}

\begin{frame}
\frametitle{Targeted Training}
	\begin{itemize}
	\item Female entrepreneurs
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	\begin{itemize}
	\item Young entrepreneurs
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	\begin{itemize}
	\item Gazelles
	\vspace{0.1in}
	\end{itemize}
\end{frame}

%---------------------

\begin{frame}
\frametitle{On-site Consulting}
	\begin{itemize}
	\item ?
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{On-site Consulting}
	\begin{itemize}
	\item ?
	\vspace{0.1in}
	\end{itemize}
\end{frame}

%---------------------

\begin{frame}
\frametitle{Complementary Constraints}
	\begin{itemize}
	\item McKenzie cash paper
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Complementary Constraints}
	\begin{itemize}
	\item McKenzie cash paper
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\subsection{Measurement of Firm Performance}

\begin{frame}
\frametitle{Imprecision of Outcome Measures}
	\begin{itemize}
	\item Confidence Intervals, pic?
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-reports}
	\begin{itemize}
	\item Self-reports of aggregate
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-reports}
	\begin{itemize}
	\item Disaggregating quantities in self-reports
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-report}
	\begin{itemize}
	\item Direct measures
	\vspace{0.1in}
	\end{itemize}
\end{frame}

%---------------------

\begin{frame}
\frametitle{Sales vs. Profits}
	\begin{itemize}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Sales vs. Profits}
	\begin{itemize}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

% ---------------------

\begin{frame}
\frametitle{?}
	\begin{itemize}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{?}
	\begin{itemize}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\subsection{Mechanisms}

\begin{frame}
\frametitle{Heterogeneity of Impact}
	\begin{itemize}
	\item Heterogeneity of treatment effect poorly understood across different approaches
	\item Potential constraints are manifold, and likely context-dependent
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Education}
	\begin{itemize}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Family Commitments}
	\begin{itemize}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Identity Concerns}
	\begin{itemize}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Aspirations}
	\begin{itemize}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Local Relevance of Best Practices}
	\begin{itemize}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\subsection{Alternative Approaches}

\begin{frame}
\frametitle{Local Knowledge}
	\begin{itemize}
	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Local Knowledge}
	\begin{itemize}
	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Local Knowledge}
	\begin{itemize}
	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
	\vspace{0.1in}
	\end{itemize}
\end{frame}

%---------------------

\begin{frame}
\frametitle{Role Models}
	\begin{itemize}
	\item La Ferrara!
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Role Models}
	\begin{itemize}
	\item La Ferrara!
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Role Models}
	\begin{itemize}
	\item La Ferrara!
	\vspace{0.1in}
	\end{itemize}
\end{frame}

%\setbeamertemplate{sidebar right}{}
\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}

\subsection{Takeaways}

\begin{frame}
\frametitle{Takeaways}
	\begin{itemize}
    \item
   	\vspace{0.10in}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Questions}
	\begin{itemize}
	\item Any questions?
	\vspace{0.2in}
	\item[] .. before we move on to our paper?
	\end{itemize}
\end{frame}

%-----------------------------------------------------------
%------------------------------------------------------------
%------------------------------------------------------------
%------------------------------------------------------------
%------------------------------------------------------------

\addtocontents{toc}{\protect\setcounter{tocdepth}{99}}

@@

\author[Dalton, R{\"u}schenp{\"o}hler, Uras, and Zia]
{Patricio S. Dalton\inst{1}\
Julius R{\"u}schenp{\"o}hler\inst{2}
Burak Uras\inst{1}\\and
Bilal Zia\inst{3}}

\institute[]{
\inst{1} Tilburg University\\
\bigskip
\inst{2} CEGA, UC Berkeley\\
\bigskip
\inst{3} The World Bank}

@@

%\setbeamertemplate{sidebar right}{}

\section{\textbf{PART II: Paper} \\ \quad \emph{Curating Local Knowledge}}

@@

\setbeamertemplate{sidebar right}[sidebar theme]
